Copy files from build-website to qblog

### 2025-03-24 src/copy-files.qmd
Added wikipedia-white-space
Updated copy-files to also read 2025 pages

---
title: "Copy files from build-website to qblog"
author: "Steve Simon"
format: html
---

@@

```{r}
#| label: locations
old_path <- "../text"
old_directories <- c("99", paste0("0", (0:9)), 10:24)
new_path <- "../../qblog/posts"
file_pattern <- "md$"
```

>>>>

---
title: "Copy files from build-website to qblog"
author: "Steve Simon"
format:
  html:
    embed-resources: true
---

@@

```{r}
#| label: locations
old_path <- "../text"
old_directories <- c("99", paste0("0", (0:9)), 10:25)
new_path <- "../../qblog/posts"
file_pattern <- "md$"
```
